Can Cultural Transmission Explain The Evolution of Cooperative Behavior?

### 2020-05-30 ms/main.tex
horizontal_and_obliuqe_results

In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes:
\begin{equation} 
\begin{split}\label{eq:nextgen_parents_oblique_only}
p' = p^2\cdot(T_B-T_A) + p\cdot(1+T_A-T_B)
\end{split}
\end{equation}

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).

>>>>

In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes
\begin{equation} 
\begin{split}\label{eq:nextgen_parents_oblique_only}
p' = p^2\cdot(T_B-T_A) + p\cdot(1+T_A-T_B)
\end{split}
\end{equation}

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).

\textbf{With vertical transmission $0<v<1$}
In this case we will not look for global fixation as we did in previous cases.
For simplicity, we will invsetigate local equilibriums. We will use eq.~\ref{eq:nextgen_adults_slimpify}
and eq.~\ref{eq:nextgen_parents_simplified} and substitute it in eq.~\ref{eq:horizontal}.
We are looking for the equilibrium $p^*$ which happens when $\hat{p}' = \hat{p}$ and we get
\begin{equation} \label{eq:oblique_and_vertic_result}
  \hat{p}^* =  \frac{\alpha bvT_A + cvT_B + T_A-T_B}{\alpha bv\cdot(T_A-T_B)- b\cdot(T_A-T_B) - cv\cdot(T_A-T_B) + c\cdot(T_A-T_B)}
\end{equation}
